How is experience transformed into memory?

### 2018-09-02 paper/main.tex

\subsection*{Participants and Experimental Design}
Participants ($n=17$) viewed the first 50 minutes of ``A Study in Pink'', an episode of the BBC series, \textit{Sherlock}. Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the \textit{Sherlock} episode in their original order and in as much detail as possible. During the entire experiment, participants were in an fMRI scanner. For comprehensive details of the experimental procedures, please refer to \cite{ChenEtal17}.
%NOTE: is this sufficient or should i provide more detail?

\subsection*{Fitting the topic model to the video text and recall transcripts}
A topic model was used to estimate the most likely mixture of topics for a given sample of text. First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed. For each scene, we considered the following features: narrative details (a sentence or two describing what happened in that scene), whether the scene was indoor or outdoor, name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and text on the screen. We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene. We then transformed the text descriptions into overlapping windows of 50 scene segments. For example, the first text sample comprised the text from the first 50 segments, the 2nd comprised the text from n+1:n+51, and so on. We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal18}.  First, the text was transformed into a vector of word counts (after removing English stopwords). This gave a word count vector for each scene in the video.  Then, the word count vectors were used to fit a topic model (topics=100, method=`batch'). We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix. The scene descriptions often spanned multiple timepoints (i.e., TRs). To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned. After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).

To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.  We transformed the list of overlapping recall sentences using the model that was trained on the video text (as described in the paragraph above). The result of this was a sentences (range: 68-294) by topics (100) matrix for each participant that represented the most likely mixture of topics for a given chunk of sentences.

\subsubsection*{Choosing topic model parameters}
There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.  To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500. Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modeling, averaging within event, etc). While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
%NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.  The reason I bring this up is that the correlations between some of the memory metrics (k, precision, distinctiveness) and hand annotated accuracy could be biased because we searched for the optimal parameters. Its not `the same' measure, but they are related to each other, so we'll have to be extra careful not to over interpret the correlations in this study.

>>>>

\subsection*{Participants and Experimental Design}
Data were collected by \cite{ChenEtal17}.  In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).  The stimulus was divided into a 23 minute and a 25 minute segment to facilitate technical issues related to the scanner.  After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the movie in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better. They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it. Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.

\subsection*{Modeling the dynamic content of the video and recall transcripts}
\subsubsection*{Topic modeling}
The input to the topic model we trained to characterize the dynamic content of the video comprised hand-generated annotations of each of 1000 scenes spanning the video clip~\citep[generated by][]{ChenEtal17}.  The features included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.  We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.  We then re-organized the text descriptions into overlapping sliding windows spanning 50 scenes each. In other words, the first text sample comprised the combined text from the first 50 scenes (i.e., 1--50), the second comprised the text from scenes 2--51, and so on.  We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18}.  Specifically, we use the \texttt{CountVectorizor} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.  We then use the \texttt{LatentDirichletAllocatin} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.  The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.  Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.  For each fMRI volume, we took the topic proportions from whatever scene was displayed for most of that volume's 1500~ms acquisition time.  This yielded a new number-of-TRs (1976) by number-of-topics (100) topic proportions matrix.

We created similar topic proportion matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.  We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; we in turn transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).  We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.  This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.  These reflected the dynamic content of each participant's recalls.

\paragraph*{Choosing topic model parameters}
\textbf{JRM NOTE: NEED TO DISCUSS THIS SECTION.  ALSO, I HAVE NOT EDITING THE WORDING.}
There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.  To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500. Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modeling, averaging within event, etc). While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
%ACH NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.  The reason I bring this up is that the correlations between some of the memory metrics (k, precision, distinctiveness) and hand annotated accuracy could be biased because we searched for the optimal parameters. Its not `the same' measure, but they are related to each other, so we'll have to be extra careful not to over interpret the correlations in this study.

\textbf{JRM STOPPED HERE}
